
\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.73]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Pratyaksh} % Your first name
\familyname{Sharma} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{Room 40, Hostel 2}{IIT Bombay, Mumbai - 400076}
\mobile{(+91) 720 804 9809}
\phone{(+1) 413 889 1707}
%\fax{(000) 111 1113}
\email{pratyaksh@cse.iitb.ac.in}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2012--Present}{Bachelor of Technology (Honors)}{\href{http://www.iitb.ac.in/}{Indian Institute of Technology}}{Bombay}{}{Major: Computer Science and Engineering \\ Minor: Applied Statistics and Informatics \\ \textit{Current GPA -- 9.24}}  % Arguments not required can be left empty

\section{Research Experience}

\cvitem{Title}{\emph{Weighted Best-First Search for W-optimal Solutions over Graphical Models}}
\cvitem{Supervisors}{Professor \href{www.ics.uci.edu/~dechter/}{Rina Dechter} \& \href{http://www.informatik.uni-trier.de/~ley/pers/hd/f/Flerova:Natalia}{Natalia Flerova}, \emph{\href{http://ics.uci.edu}{University of California, Irvine}}}
\cvitem{Description}{Performed empirical analysis of \textbf{anytime weighted best first strategies on AND/OR search spaces} for approximate inference. Compared the effects of Mini-bucket Elimination, Join-Graph Linear Programming(JGLP) and MBE with moment matching (MBE-MM) heuristics on search performance. Participated in the \textbf{\href{http://www.hlt.utdallas.edu/~vgogate/uai14-competition/}{UAI 2014 - Probabilistic Inference Competition}} with the studied solver. \newline Published in the proceedings of Planning, Search and Optimization (PlanSOpt) workshop, AAAI'15.\newline \emph{Url:} \url{http://www.ics.uci.edu/~dechter/publications/r216.pdf}}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Key Projects}

\cventry{Aug 2014 - Nov 2014}{Sentiment analysis of song lyrics for genre identification}{}{}{\newline Supervisor: \href{http://www.cse.iitb.ac.in/~pb/}{Prof. Pushpak Bhattacharyya}, IIT Bombay}{Developed a system to analyse song lyrics and output the mood/emotion/sentiment associated with the song. Classifying a song solely based on its lyrics is a challenging problem and existing approaches yield poor accuracy. 
}

%------------------------------------------------

\cventry{Sept 2014 - Nov 2014}{Searchable Symmetric Encryption}{}{}{\newline Supervisor: \href{http://www.cse.iitb.ac.in/~bernard/}{Prof. Bernard L. Menezes}, IIT Bombay}{Developed a dynamic searchable symmetric encryption application with powerful regex search capabilities. Further work is to study the attacks possible (and countermeasures) in this setting.}

%------------------------------------------------

\cventry{Jan 2013 - Apr 2013}{Che.ss}{A chess engine in PLT Scheme}{}{\newline Supervisor: Prof. Amitabha Sanyal, IIT Bombay}{Programmed a chess engine in the functional paradigm. The minimax algorithm with $\alpha-\beta$ pruning formed the basis of AI. The heuristics involved use of Piece-Square tables, analyzing pawn structure and various other chess tactics. Used the XBoard GUI and wrote a parser/translator for the Chess Engine Communication Protocol. Also investigated other chess algorithms like Negascout and MTD-f.}

%------------------------------------------------


\cventry{Mar 2014 - Apr 2014}{Simulation in Box2D}{}{}{\newline Supervisor: Prof. Prof. Parag Chaudhuri, IIT Bombay}{Developed a complex simulation of a locomotive in the Box2D Physics Engine. \newline
\emph{Url:} \url{https://github.com/pratyakshs/Box2D-SteamEngine}}



%---------------------------------------------------------------------------
%	OTHER PROJECTS
%--------------------------------------------------------------------------
\section{Other Projects}



\cventry{Jul 2013 - Sep 2013}{Analytics developer}{\href{http://coursewave.org/}{Coursewave.org}, an online courseware startup}{}{}{Developed live data visualizations for students and teachers using various web APIs
and integrated the user analytics with online test taking interface.}


\cventry{Aug 2013}{News clustering hack}{Yahoo! HackU}{}{}{Prototype for clustering similar news content in Yahoo! News results using several Yahoo! APIs like BOSS, YQL and YUI}

\cventry{Mar 2014}{JTalk - P2P chat program}{}{}{}{Developed a text based LAN messenger in Java using multiple threads and the Swing library. 
\newline \emph{Url:} \url{https://github.com/pratyakshs/JTalk}
}

\cventry{Nov 2012}{Pac-man}{}{}{Guide: Prof. Abhiram Ranade}{Recreated the classic game of pac-man using in C++ using the SimpleCpp/EzWindows graphics library.
Programmed the deterministic ghost behaviour as in the standard game.
}



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2013}{Honourable Mention at ACM-ICPC Amritapuri Regionals, ranked 24th in India}

\cvitem{2012}{All India Rank 33 in IIT Joint Entrance Examination out of over 500,000 candidates}
\cvitem{2012}{All India Rank 29 in AIEEE 2012 out of over 1,200,000 candidates}

\cvitem{2012}{Qualified for Indian National Physics (INPhO), Chemistry (INChO) and Astronomy (INAO) Olympiads (among top 300 students in India in each subject)}

\cvitem{2012}{Awarded Gold medal by DPS Society for maintaining excellent academic record for seven consecutive years}


\cvitem{2011}{Cleared regional stage of Indian National Mathematics Olympiad (INMO)}

\cvitem{2011}{Awarded the KVPY fellowship by Department of Science and Technology, Government of India, to take up a career in research
}


\cvitem{2010}{Admitted to the Education Program for Gifted Youth (EPGY) Summer
Institutes High School Program at Stanford University}



%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technical skills}

\cvitem{Programming Languages}{C/C++, Python, Java, PLT Scheme, Prolog, Bash, MIPS32, VHDL}
\cvitem{Web}{HTML, CSS, Javascript, PHP, JSP, MySQL, PostgreSQL, AJAX, JSON}
\cvitem{Tools and Libraries}{Sage, \LaTeXe , Scilab, PSPICE, Mathematica, Numpy, R, Octave, Boost C++}
\clearpage
%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR ACTIVITES SECTION
%----------------------------------------------------------------------------------------

\section{Extracurricular Activites}
\cvitem{}{Active participant in algorithmic coding contests on online judges (\href{http://spoj.com/users/pratyaksh}{SPOJ}, \href{codeforces.com/profile/pratyaksh}{Codeforces})}
\cvitem{2013}{Stood 17th (2nd among teams from IIT-B) in online round of ACM ICPC Regionals}
\cvitem{2013}{Coordinator at Mood Indigo and Techfest,  IIT Bombay}
\cvitem{2011}{Invited to Vijyoshi camp (2011) at IISc Bangalore}
\cvitem{2011}{Attended the summer program for KVPY fellows at IISER Mohali}
\cvitem{2011}{Served as Vice-President of Axiom (school mathematics society) and was responsible for the execution of Axiom 2011 (second largest inter-school mathematics symposium in Delhi) and won several inter-school mathematics competitions}
\cvitem{2012}{Ranked 2nd in IIT-Bombay in Maths and Physics Quiz}
\cvitem{2012-13}{Served one year under the National Service Scheme (NSS)}


%----------------------------------------------------------------------------------------
%	COURSES SECTION
%----------------------------------------------------------------------------------------

\section{Relevant Courses}

\cvitem{Computer Science}{Computer Architecture*, Computer Networks*, Database Systems*, Natural Language Processing*, Network Security and Cryptography*, Design and Analysis of Algorithms, Introduction to Machine Learning, Data Structures and Algorithms, Abstractions and
Paradigms in Programming, Discrete Structures, Graph Theory, Number Theory and Cryptography, Automata Theory and Logic, Logic
Design, Software Systems Laboratory}

\cvitem{Statistics and Mathematics}{Statistical Inference*, Games and Information*, Calculus, Linear Algebra, Differential Equations, Data Analysis and Interpretation, Probability Theory, Combinatorics, Numerical Analysis, Introduction to Derivative Pricing}

\cvitem{Other}{Introduction to Electrical and Electronic Circuits, Modern Physics, Economics, Experimental and Measurement Laboratory}


\end{document}
